\documentclass[12pt,a4paper]{report}

\usepackage[utf8]{inputenc} %usa il formato utf8 per l'encoding
\usepackage[T1]{fontenc} % usa un font ragionevole
\usepackage{lmodern} % migliora alcuni dettagli della visualizzazione del font
\usepackage{todonotes} %questo serve per mettere le note

\usepackage[nottoc]{tocbibind}%mette la bibliografia nella table of contents
\usepackage[graphicx]{realboxes}%per ruotare le tabelle
\usepackage{adjustbox}
\usepackage{geometry}
\usepackage{longtable}
\usepackage{float}
\usepackage{titlesec}
\usepackage{amssymb,amsmath}
\usepackage{amsthm}
\usepackage[]{graphicx} \graphicspath{ {Fig/} }
\usepackage{caption}
\usepackage[]{xcolor}
\usepackage{booktabs, multirow}
\usepackage[colorlinks,linkcolor=black,urlcolor=blue,citecolor=gray]{hyperref}
\usepackage{natbib}
\usepackage{url}
\usepackage{lineno}
\usepackage{subfig}
\usepackage{graphicx}

\usepackage{subfig}
\usepackage[italian, english]{babel}  %%% !!! Cancellare 'english' per avere "Sommario, Capitolo..." !!!

%------------------------------------------------------------------------------------
% questi non dovrebbero servirti, in particolare con i pacchetti che ho aggiunto
\newcommand{\eg}{\`e}
\newcommand{\ea}{\'e}
\newcommand{\Eg}{\`E}
\newcommand{\og}{\`o}
\newcommand{\ag}{\`a}
\newcommand{\ug}{\`u}
\newcommand{\ig}{\`{\i}}
\newcommand{\R}{\textsf{R}}
\newcommand{\Fortran}{\textsf{Fortran}}
%------------------------------------------------------------------------------------
\definecolor{MyGray}{rgb}{0.30,0.31,0.32} % definizione grigio
\definecolor{MyDarkBlue}{rgb}{0.,0.08,0.5} % blu scuro
\definecolor{MyLightBlue}{rgb}{0.2,0.2,1.0} % blu chiaro
\definecolor{MyDarkRed}{rgb}{0.5,0.04,0} % rosso scuro
\definecolor{MyDarkGreen}{rgb}{0.0,0.4,0.08} % verde scuro
\definecolor{SectionBlue}{rgb}{0.16,0.32,0.75} % blu per sezioni
\definecolor{SubSectionBlue}{rgb}{0.0,0.53,0.74} % blu per sottosezioni
\definecolor{SubSubSectionBlue}{rgb}{0.0,0.58,0.65} % blu per sottosottosezioni
%------------------------------------------------------------------------------------
\titleformat{\chapter}[display]
  {\color{SectionBlue}\normalfont\LARGE\bfseries}{\chaptertitlename\ \thechapter}{20pt}{\Huge}
\titleformat{\section}
{\color{SectionBlue}\normalfont\Large\bfseries}
{\color{SectionBlue}\thesection}{1em}{}
\titleformat{\subsection}
{\color{SubSectionBlue}\normalfont\Large\bfseries}
{\color{SubSectionBlue}\thesubsection}{1em}{}
\titleformat{\subsubsection}
{\color{SubSubSectionBlue}\normalfont\large\bfseries}
{\color{SubSubSectionBlue}\thesubsubsection}{1em}{}
\DeclareCaptionFont{myblue}{\color{SubSectionBlue}}
\captionsetup{labelfont={myblue,bf}}
%------------------------------------------------------------------------------------
\newcommand{\myboldverb}[1]{{\color{MyDarkBlue}\bfseries{#1}}} % per enfasi in grassetto
\newcommand{\myverb}[1]{{\color{MyDarkBlue}\texttt{#1}}} % in evidenza
\newcommand{\myurl}[1]{{\color{MyDarkGreen}\url{#1}}} % per url
\newcommand{\quotesection}[1]{{\color{SectionBlue}\textbf{Sezione \ref{#1}}}}
\newcommand{\quotesubsection}[1]{{\color{SubSectionBlue}\textbf{Sezione \ref{#1}}}}
\newcommand{\quotesubsubsection}[1]{{\color{SubSubSectionBlue}\textbf{Sezione \ref{#1}}}}
\newcommand{\quotefigure}[1]{{\color{MyDarkGreen}\textbf{Figura \ref{#1}}}}
\newcommand{\quotetable}[1]{{\color{MyDarkGreen}\textbf{Tabella \ref{#1}}}}

\newcommand{\covid}{\textit{Sars-COVID19} } %comando covid
\newcommand{\death}{{\scshape Death} } %comando Morte
\newcommand{\icu}{{\scshape ICU Admission} } %comando ICU
\newcommand{\orsola}{\textit{IRCSS Azienda ospedaliero-universitaria di Bologna - Policlinico Sant'Orsola-Malpighi} }
%--------------------------------------------------------------------------------------
\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]

\theoremstyle{remark}
\newtheorem*{remark}{Remark}

\graphicspath{ {./imgs/} }


%------------------------------------------------------------------------------------
\geometry{
	paper=a4paper, % Change to letterpaper for US letter
	inner=2.5cm, % Inner margin
	outer=3cm, % Outer margin
	bindingoffset=0.5cm, % Binding offset
	top=2.5cm, % Top margin
	bottom=3cm, % Bottom margin
	%showframe, % Uncomment to show how the type block is set on the page
}


%------------------------------------------------------------------------------------
%------------------------------ HERE WE GO ------------------------------------------
%------------------------------------------------------------------------------------


\textwidth=450pt\oddsidemargin=0pt
\begin{document}
\begin{titlepage}
\begin{center}
{{\Large{\textsc{Alma Mater Studiorum $\cdot$ University of  Bologna}}}} 
\rule[0.1cm]{15.8cm}{0.1mm}
\rule[0.5cm]{15.8cm}{0.6mm}
\\\vspace{3mm}
{\small{\bf School of Science \\
Department of Physics and Astronomy\\
Master Degree in Physics}}
\end{center}

\vspace{23mm}

\begin{center}\textcolor{black}{
{\LARGE{\bf COVID-19 prognosis estimation from CAT scan radiomics: comparison of different machine learning approaches for predicting patients survival and ICU Admission}}\\
}\end{center}

\vspace{50mm} \par \noindent

\begin{minipage}[t]{0.47\textwidth}
{\large{\bf Supervisor: \vspace{2mm}\\\textcolor{black}{
Prof. Enrico Giampieri}\\\\
\textcolor{black}{
\bf Co-supervisor:\vspace{2mm}\\
Dr. Lidia Strigari\\\\}}}
\end{minipage}
%
\hfill
%
\begin{minipage}[t]{0.47\textwidth}\raggedleft \textcolor{black}{
{\large{\bf Submitted by:
\vspace{2mm}\\
%
% INSERT THE NAME OF THE GRADUAND
%
\textcolor{black}{
Lorenzo Spagnoli}}}
}
\end{minipage}

\vspace{40mm}

\begin{center}
%
% INSERT THE ACADEMIC YEAR
%
Academic Year \textcolor{black}{2020/2021}
\end{center}

\end{titlepage}

\thispagestyle{empty}
%\newpage
%\listoftodos
%-------------------------------------ABSTRACT
%\thispagestyle{empty}
\vspace*{5cm}
\renewcommand{\abstractname}{\color{MyDarkBlue}{Abstract}}
\begin{abstract}
%Useful diagnostic vs prognostic and data- vs law-driven given in \cite{1} page 18.

Since the start of 2020 \covid has given rise to a world-wide pandemic.
In an attempt to slow down the fast and uncontrollable spreading of this disease various prevention and diagnostic methods have been developed.
In this thesis, out of all these various methods, the attention has been put on Machine Learning methods used to predict prognosis that are based, for the most part, on data originating from medical images.

The techniques belonging to the field of radiomics have been used to extract information from images segmented using a software available in the hospital that provided the clinical data as well as the images.
The usefulness of different families of variables has then been evaluated through their performance in the methods used, namely Lasso regularized regression and Random Forest.
Dimensionality reduction techniques have also been used to attain a better understanding of the dataset at hand.

Following a first introductiory chapter in the second chapter a basic theoretical overview of the necessary core concepts that will be needed throughout this whole work will be provided and then the focus will be shifted on the various methods and instruments used in the development of this thesis.
The third is going to be a report of the results and finally some conclusions will be derived from the previously presented results.
It will be concluded that the segmentation and feature extraction step is of pivotal importance in driving the performance of the predictions.
In fact, in this thesis, it seems that the information from the images achieves the same predictive power that can be derived from the clinical data.
This can be interpreted in three ways: first it can be taken as a symptom of the fact even the more complex \covid cases can be segmented automatically, or semi-automatically by untrained personnel, which will leading to competing results with other methodologies.
Secondly it can be taken to show that the performance of clinical variables can be reached by radiomic features alone in a semi-automatic pipeline, which could aid in reducing the workload imposed on medical professionals in case of pandemic.
Finally it can be taken ass proof that the method has room to improve the performances by more carefully investing in the segmentation phase.


\end{abstract}
%-------------------------------------INDEX
\setcounter{page}{1}
\pagenumbering{roman}
\tableofcontents{}
%\vspace*{2cm}
%\setcounter{page}{1}
%\pagenumbering{arabic}

\linenumbers
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Chapter 1: introduction
\include{Introduction}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Chapter 2:
\include{Materials_metodologies}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Chapter 3
\include{Results}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Chapter 4
\include{Conclusions}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Chapter 5
\include{Appendix}

%-------------------------------------REFERENCES

\nocite{*}
\bibliographystyle{abbrv}
\bibliography{biblio}

\end{document}
